Web Service Community \\ Learning

### 2014-06-13 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Recent work have emphasized on motivation and benefits of communities of web services[references]. Communities of web services facilitate discovery of web services, improve the quality of service, and also help individual services find better market share and opportunities. A community master or coordinator is also responsible for \emph{community development}. Community development is about finding the right web service for the community, satisfying all web services and community coordinators involved within the community, which is a challenging task. Many ideas have been proposed to tackle this problem. Some of these work have complex on demand algorithms [3way, coopchina, ourwork] and in order to make it feasible they have simplified the task to make the algorithm executable on-demand or they have simplified the constraints, ignoring important aspects of the problem. For example in [coopchina] a simple egalitarian way of distributing gain which completely ignores gain for collaborative work, instead of complex shapely-value which considers gain for all subset of agents working together which basicly ignores the most important criteria of finding optimal group, has been proposed. Other category of related work exists which they do not focus on all parties involved within the community [2player]. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity which makes decision making impossible in an on-demand fashion or they simplify important aspects to make it practical in real world hurting the decision making performance.

In this paper, we have implemented [OurMethodName] in which we initially train our services in different possible communities and let them experiment and check the outcome of different scenarios. Based on the trained results these services can be utilized with efficient methods of foreseeing how each of their decisions would impact their long term and short term goals, therefore opting for best decision available.

Web services have different set of features. These features are derived from quality metrics of web services. The values of these features influences the utility of the web services and when collaborating with our web services, these set of features determines the utility and performance of community. Having a set of web services with pre-defined set of features, we let web services evaluate performance of collaboration with a small subset of other web services. Keeping a history of the output estimate of this collaboration, each web service individually will be utilized with knowledge of collaboration with web services having different set of feature values. We keep this history and train web services so they can deduct how they would perform collabration with new web services having new set of feature values. By deploying a linear distant function, the web services will be able to predict the outcome of collaboration with different web services which may not have been collaborated in during training process.

>>>>

Recent work have emphasized on motivation and benefits of communities of web services [references]. This is due to the fact that communities facilitate discovery of web services, improve the quality of service, and help individual services find better market share and opportunities. The challenge is then community development, which is finding the right web service for the community, satisfying all web services and community coordinators involved within the community. This is also a challenge from individual web service side in the sense that a web service seeks for communities to interact with and obtain best outcome. Towards addressing these issues, there have been a number of proposals. Some of these works propose complex models on demand algorithms [3way, coopchina, ourwork] to effectively find target points. But they have to simplify the algorithm by limited parameters in order to make it feasible and algorithm executable. The simplifications problem some times negatively influences the outcome in the sense that simplifying the constraints may cause ignoring important aspects of the problem. For example [coopchina] proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work instead of complex shapely-value. This model considers gain for all subset of agents working together, which basically ignores the most important criteria of finding optimal group. Other category of related work exists which they do not focus on all parties involved within the community [2player]. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in real world hurting the decision making performance.

In this paper, we have implemented [OurMethodName] using which, we initially train web services in different possible communities and let them experiment and check the outcome of different scenarios with respect to their internal functional and external cooperative characteristics. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, the trained results equip web services with efficient methods of foreseeing how their choices of actions would impact their long term and short term goals, therefore opting for best decision available.

In further details, the proposed learning method is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data set (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering these features, we gathered functional and cooperative features for both individual web services and communities in 60 different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in training model. Using cross validation set, web services are able to compute optimal hypothesis function (using logistic regression) that can be used to predict outcome out of cooperative work with other individual web services or communities. Our findings show that web services equipped with this framework have by far better outcome in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.
